Global land characterisation using land cover fractions at 100 m resolution

### 2021-02-04 article/highlights.tex
Move parts to appendix

\documentclass[review,authoryear,3p]{elsarticle}
\journal{Remote Sensing of Environment}
\begin{document}
\section*{Highlights}
\begin{itemize}
    \item 4 machine learning model groups tested for deriving 7 land cover fractions globally
    \item Multi-step approach proposed for dealing with zero inflation in fraction data
    \item Random forest regression performed the best
    \item Optical remote sensing data was the most important input for model predictions
    \item Multi-fraction land cover mapping shown as an alternative to discrete classification
\end{itemize}

>>>>

\documentclass[review,authoryear,3p]{elsarticle}
\journal{Remote Sensing of Environment}
\begin{document}
\section*{Highlights}
\begin{itemize}
    %\item 4 machine learning model groups tested for deriving 7 land cover fractions globally
    \item 7 land cover fractions derived globally using machine learning algorithms
    \item Multi-step approach proposed for dealing with zero inflation in fraction data
    %\item 1234567890123456789012345678901234567890123456789012345678901234567890123456789012345
    \item The approach provides a middle ground between discrete and fractional mapping
    \item The approach gives the best guess and improves estimation of 0\% and 100\% fractions
    \item Comprehensive spatial accuracy assessment based on over 20\,000 points
    \item Multi-fraction land cover mapping shown as an alternative to discrete classification
\end{itemize}
